Dynamics of thin liquid film flows studied with the lattice Boltzmann method

### 2022-12-06 others/abstract.tex
jens_comments_work

\begin{abstract}
\section*{Abstract}
Fluid dynamics is a part of our everyday life.
The governing equations describe not only large weather systems on planetary scales ($10^6$m) but also reach down to wetting problems on the nanometric scale ($10^{-9}$m). 
That a single theory can describe both the movement of atmospheric layers as well as the displacement of the contact line of a droplet with a diameter smaller than a micron ($10^{-6}$m) is highly non trivial and related to the scale invariant nature of flow problems.

The lubrication approximation was first thought of by Osborn Reynolds in the $19^{\text{th}}$ century. 
He understood that in the case of a single small dimension the Navier-Stokes equations can be simplified.
Since then the functional formulation of the lubrication approximation the so called thin film equation has shed new light on diverse problems.

>>>>

\begin{abstract}
\section*{Abstract}
Fluid dynamics is a part of our everyday life.
The governing equations describe not only large weather systems on planetary scales ($10^6$m) but also reach down to wetting problems on the nanometric scale ($10^{-9}$m). 
That a single theory can describe both the movement of atmospheric layers as well as the displacement of the contact line of a droplet with a diameter smaller than a micrometer ($10^{-6}$m) is highly non trivial and related to the scale invariant nature of flow problems.

The lubrication approximation was first thought of by Osborn Reynolds in the $19^{\text{th}}$ century. 
He understood that a lubrication layer is essentially a thin layer of fluid between mechanical components.
This thin layer offered some novelties which made it possible to simplify the Navier-Stokes equation.
From that time onwards the functional formulation of the lubrication approximation, the so-called thin film equation, has shed new light on problems such as wetting, coating and printing to name but a few.
